### 2017-06-29 paper.tex
Merging

@@

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Referring back to Rule~1,
it can sometimes be difficult for lesson developers to understand the frame of a given learner,
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.

>>>>

\begin{mdframed}

\noindent
Box 1: Learner Profile

Jorge has just moved from Costa Rica to Canada to study agricultural engineering.
While fluent in both Spanish and English,
he has a hearing disability that sometimes makes it hard for him to understand lectures,
particularly in noisy environments.
Other than using Excel, Word, and the Internet,
Jorge's most significant previous experience with computers is
helping his sister build a WordPress site for the family business.

Jorge needs to measure properties of soil from nearby farms
using a handheld device that sends text files to his computer.
Right now, Jorge has to open each file in Excel,
crop the first and last points,
and calculate an average.
This workshop will show Jorge how to write a little Python program
to read the data,
select the right values from each file,
and calculate the required statistics.

\end{mdframed}

@@

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Referring back to Rule~1,
it can sometimes be difficult for lesson developers to understand the frame of a given learner,
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.
This is one example of a larger guideline:
when processing feedback,
separate items that apply to specific lessons (and can guide its future development)
from those that are better tackled elsewhere
(e.g., by developing new lessons or through organizational change).
